Attribute fusion in a latent process model for time series of graphs

### 2011-05-17 ssp2011.tex
Add section on number of triangles

@@

  \tau_\lambda(G(t)) = \sum_{k=1}^{K} \lambda_k \!\! \sum_{(u,v,w) \in
    \binom{V}{3}} h_k(u,v,w) \\

@@

where $h_k(u,v,w)$ is the indicator function that the argument, a set
of three vertices, forms a triangle of type $k$. A triangle
is of type $k$ provided that all edges in the triangle have attribute
$k$. \\ \\

@@

@@

concerned with adpating the results in

>>>>

\def\mathllap{\mathpalette\mathllapinternal}
\def\mathllapinternal#1#2{%
\llap{$\mathsurround=0pt#1{#2}$}% $
}
\def\clap#1{\hbox to 0pt{\hss#1\hss}}
\def\mathclap{\mathpalette\mathclapinternal}
\def\mathclapinternal#1#2{%
\clap{$\mathsurround=0pt#1{#2}$}%
}
\def\mathrlap{\mathpalette\mathrlapinternal}
\def\mathrlapinternal#1#2{%
\rlap{$\mathsurround=0pt#1{#2}$}% $
}

@@

  \tau_{\lambda}(t) = \sum_{(i,j,k) \in K^{3}\vphantom{\tbinom{V}{3}}}
  \, \, \sum_{(u,v,w)
      \in \tbinom{V}{3}} \lambda_{i}\lambda_j \lambda_k h_{ijk}(u,v,w) \\

@@

where $h_{ijk}(u,v,w)$ is the indicator function that $u$, $v$, and
$w$ form a triangle whose edges have attributes $i$, $j$, and $k$. \\ \\

@@

\subsection{Power estimates for $\tau_{\lambda}(t)$}
The limiting distribution for the number of triangles in unattributed
\cite{nowicki88:_subgr_u_statis_method} for the Erd\"{o}s-Renyi model
and in \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}
for the kidney-egg model.  
\label{sec:power-estim-tau_l}
  \label{thm:4}
  Let $\rho$ and $\varsigma$ be defined by
    \label{eq:42}
    \rho = \tbinom{m}{3} \langle \lambda, \pi_{AA} \rangle^{3} &+
    \tbinom{m}{2}(n-m) \langle \lambda, \pi_{AA} \rangle \langle
    \lambda, \pi_{0A} \rangle^{2} \\ &+ m \tbinom{n-m}{2} \langle \lambda,
    \pi_{0A} \rangle^{2} \langle \lambda, \pi_{00} \rangle \\ &+
    \tbinom{n-m}{3} \langle \lambda, \pi_{00} \rangle^{3}
    \varsigma^{2} &= \tbinom{m}{2} \langle \lambda, \eta_{AA} \lambda
    \rangle \Bigl[(m-2) \langle \lambda, \pi_{AA} \rangle^{2} + (n-m)
    \langle \pi_{0A} \rangle^{2} \Bigr]^{2} \\
    &+ m(n-m) \langle \lambda, \eta_{0A} \lambda \rangle^{2} \Bigl[(m-1)
    \langle \lambda, \pi_{AA} \rangle + (n-m-1) \langle \lambda, \pi_{00} \rangle \Bigr]^{2} \\
    &+ \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle
    \Bigl[m \langle \lambda, \pi_{0A} \rangle^{2} + (n-m-2) \langle
    \lambda, \pi_{00} \rangle^{2} \Bigr]^{2}
  As $n \rightarrow \infty$, we have
    \frac{\tau_{\lambda}(t) - \tbinom{n}{3}\langle \lambda, \pi_{00}
      \rangle^{3}}{(n-2) \langle \lambda, \pi_{00} \rangle^{2}
      \sqrt{\tbinom{n}{2} \langle \lambda, \eta_{00} \lambda \rangle}}
    \rightsquigarrow \mathcal{N}(0,1) \qquad \text{for $t < t^{*}$} \\
    \frac{\tau_{\lambda}(t) - \rho}{\varsigma} \rightsquigarrow
    \mathcal{N}(0,1) \qquad \text{for $t = t^{*}$}

@@

concerned with adapting the results in
